Arc Blanc: a real time ocean simulation framework

### 2024-11-12 paper.tex
Fix typo
Fixed typos for greek variable

The product between the Donelan-Banner and $\xi$ spectra is denoted by $D_{DB\xi}$, and is expressed as follows:
\begin{equation}
	D_{DB\xi}(\omega, \theta) =Q_{DB\xi}(\omega) D_{DB}(\omega, \theta) D_{\xi}(\omega, \theta)
\end{equation}
where the normalization factor is:
\begin{equation}
	Q_{DB\xi}(\omega)=\frac{1}{\displaystyle\int_{-\pi}^\pi D_{DB}(\omega, \theta) D_{\xi}(\omega, \theta) \mathrm{d} \theta}.
\end{equation}
This normalization factor $Q_{DB\xi}(\omega)$ is computationally expensive.

@@

Note that we applied a first normalization factor $Q_{DB}$ to the simple Donelan Banner spectrum \ref{equa:ddb} before calculating this second normalization factor $\widetilde{Q_{DB\xi}}(r_{omega})$. In fact, if we simply approximate the full-spectrum normalization factor before applying it, we'll be faced with a normalization problem, because for small values of $r_{omega}$, $Q_{DB\xi}(\omega)$ will be very low and therefore numerically difficult to normalize.

>>>>

The product between the Donelan-Banner and $D_{\xi}$ spectra is denoted by $D_{DB\xi}$, and is expressed as follows:
\begin{equation}
	D_{DB\xi}(\omega, \theta) =Q_{DB\xi}(\omega) D_{DB}(\omega, \theta) D_{\xi}(\omega, \theta)
\end{equation}
where the normalization factor is:
\begin{equation}
	Q_{DB\xi}(\omega)=\frac{1}{\displaystyle\int_{-\pi}^\pi D_{DB}(\omega, \theta) D_{\xi}(\omega, \theta) \mathrm{d} \theta}.
\end{equation}
This normalization factor $Q_{DB\xi}(\omega)$ is computationally expensive.

@@

Note that we applied a first normalization factor $Q_{DB}$ to the simple Donelan Banner spectrum (Equation \ref{equa:ddb}) before calculating this second normalization factor $\widetilde{Q_{DB\xi}}(r_{\omega})$. In fact, if we simply approximate the full-spectrum normalization factor before applying it, we'll be faced with a normalization problem, because for small values of $r_{\omega}$, $Q_{DB\xi}(\omega)$ will be very low and therefore numerically difficult to normalize.
